### 2017-10-23 paper/sections/5_implementation.tex
paper: remove popper :'(
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

% how it works in CephFS, how I used it
\subsection{Metadata Store}
\label{sec:metadata-store}

% how it works in CephFS
In CephFS, the metadata store is a data structure that represents the file
system namespace. This data structure is stored in two places: in memory ({\it
i.e.} in the collective memory of the metadata server cluster) and as objects
in the object store. In the object store, directories and their inodes are
stored together in objects to improve the performance of scans.  The metadata
store data structure is structured as a tree of directory fragments making it
easier to read and traverse.

@@

\subsection{Journal}
\label{sec:journal}

The journal is the second way that CephFS represents the file system namespace;
it is a log of metadata updates that can materialize the namespace when the
updates are replayed onto the metadata store. The journal is a ``pile system";
writes are fast but reads are slow because state must be reconstructed.
Specifically, reads are slow because there is more state to read, it is
unorganized, and many of the updates may be redundant.

@@

\subsection{Journal Tool}
\label{sec:journal-tool}

The journal tool is used for disaster recovery and lets administrators view and
modify the journal. It can read the journal, export the journal as a file,
erase events, and apply updates to the metadata store.  To apply journal
updates to the metadata store, the journal tool reads the journal from object
store objects and replays the updates on the metadata store in the object
store.

@@

\subsection{Inode Cache}
\label{sec:inode-cache}

In CephFS, the inode cache reduces the number of RPCs between clients and
metadata servers. Without contention clients can resolve metadata reads locally
thus reducing the number of operations ({\it e.g.}, \texttt{lookup()}s).  For example, if a client or
metadata server is not caching the directory inode, all creates within that
directory will result in a lookup and a create request. If the directory inode
is cached then only the create needs to be sent.  The size of the inode cache
is configurable so as not to saturate the memory on the metadata server --
inodes in CephFS are about 1400
bytes\footnote{http://docs.ceph.com/docs/jewel/dev/mds\_internals/data-structures/}.
The inode cache has code for manipulating inode numbers, such as pre-allocating
inodes to clients.

\textbf{Cudele}: ``Nonvolatile Apply" uses the internal inode cache
code to allocate inodes to clients that decouple parts of the namespace and to
skip inodes used by the client at merge time.\\

\subsection{Large Inodes}
\label{sec:large-inodes}

In CephFS, inodes already store policies, like how the file is striped
across the object store or for managing subtrees for load balancing. These
policies adhere to logical partitionings of metadata or data, like Ceph pools and file
system namespace subtrees. To implement this, the namespace data structure has
the ability to recursively apply policies to subtrees and to isolate subtrees
from each other.

>>>>

% how it works in CephFS, how I used it
%\subsection{Metadata Store}
%\label{sec:metadata-store}

% how it works in CephFS
\textbf{Metadata Store}: In CephFS, the metadata store is a data structure that represents the file
system namespace. This data structure is stored in two places: in memory ({\it
i.e.} in the collective memory of the metadata server cluster) and as objects
in the object store. In the object store, directories and their inodes are
stored together in objects to improve the performance of scans.  The metadata
store data structure is structured as a tree of directory fragments making it
easier to read and traverse.

@@

%\subsection{Journal}
%\label{sec:journal}

\textbf{Journal}: The journal is the second way that CephFS represents the file system namespace;
it is a log of metadata updates that can materialize the namespace when the
updates are replayed onto the metadata store. The journal is a ``pile system";
writes are fast but reads are slow because state must be reconstructed.
Specifically, reads are slow because there is more state to read, it is
unorganized, and many of the updates may be redundant.

@@

%\subsection{Journal Tool}
%\label{sec:journal-tool}

\textbf{Journal Tool}: The journal tool is used for disaster recovery and lets administrators view and
modify the journal. It can read the journal, export the journal as a file,
erase events, and apply updates to the metadata store.  To apply journal
updates to the metadata store, the journal tool reads the journal from object
store objects and replays the updates on the metadata store in the object
store.

@@

%\subsection{Inode Cache}
%\label{sec:inode-cache}

\textbf{Inode Cache}: In CephFS, the inode cache reduces the number of RPCs between clients and
metadata servers. Without contention clients can resolve metadata reads locally
thus reducing the number of operations ({\it e.g.}, \texttt{lookup()}s).  For example, if a client or
metadata server is not caching the directory inode, all creates within that
directory will result in a lookup and a create request. If the directory inode
is cached then only the create needs to be sent.  The size of the inode cache
is configurable so as not to saturate the memory on the metadata server --
inodes in CephFS are about 1400
bytes\footnote{http://docs.ceph.com/docs/jewel/dev/mds\_internals/data-structures/}.
The inode cache has code for manipulating inode numbers, such as pre-allocating
inodes to clients.

\textbf{Cudele}: ``Nonvolatile Apply" uses the internal inode cache
code to allocate inodes to clients that decouple parts of the namespace and to
skip inodes used by the client at merge time.

%\subsection{Large Inodes}
%\label{sec:large-inodes}

\textbf{Large Inodes}: In CephFS, inodes already store policies, like how the file is striped
across the object store or for managing subtrees for load balancing. These
policies adhere to logical partitionings of metadata or data, like Ceph pools and file
system namespace subtrees. To implement this, the namespace data structure has
the ability to recursively apply policies to subtrees and to isolate subtrees
from each other.

### 2017-10-23 paper/sections/6_results.tex
paper: remove popper :'(
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

We run experiments on the same cluster and normalize results to control for
hardware differences and to make our results more generally applicable and
reproducible\footnote{ This paper adheres to The Popper
Convention~\cite{jimenez_popper_2016}, so experiments presented here are
available in the repository for this article.  Experiments can be examined in
more detail, or even re-run, by visiting the \texttt{[source]} link next to
each figure. That link points to a Jupyter notebook that shows the analysis and
source code for that graph, which points to an experiment and its artifacts.}.
We use a CloudLab cluster of 34 nodes, each with 16 2.4 GHz CPUs, 128GB RAM,
and SSDs.  Each node uses Ubuntu 14.04 and We develop on Ceph's Jewel release,
version 10.2.1, which was released in May 2016. All daemons run as a single
process (the default setting for Ceph) and the Ceph
components\footnote{http://docs.ceph.com/docs/jewel/rados/} are: 1 monitor, 3
object storage daemons, 1 metadata server, and 29 clients.

\subsection{Microbenchmarks}
\label{sec:microbenchmarks}
\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/composable-mechanisms.png}
\caption{[\href{https://www.google.com}{source}] Performance of each
mechanism (left) and building consistency/durability guarantees (right) for
100K files creates from a single client. Results are normalized to the runtime of writing
events to the client's in-memory journal.
\label{fig:composable-mechanisms}}
\end{figure}

>>>>

%We run experiments on the same cluster and normalize results to control for
%hardware differences and to make our results more generally applicable and
%reproducible\footnote{ This paper adheres to The Popper
%Convention~\cite{jimenez_popper_2016}, so experiments presented here are
%available in the repository for this article.  Experiments can be examined in
%more detail, or even re-run, by visiting the \texttt{[source]} link next to
%each figure. That link points to a Jupyter notebook that shows the analysis and
%source code for that graph, which points to an experiment and its artifacts.}.
%We use a CloudLab cluster of 34 nodes, each with 16 2.4 GHz CPUs, 128GB RAM,
%and SSDs.  Each node uses Ubuntu 14.04 and We develop on Ceph's Jewel release,
%version 10.2.1, which was released in May 2016. All daemons run as a single
%process (the default setting for Ceph) and the Ceph
%components\footnote{http://docs.ceph.com/docs/jewel/rados/} are: 1 monitor, 3
%object storage daemons, 1 metadata server, and 29 clients.

\subsection{Microbenchmarks}
\label{sec:microbenchmarks}
\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/composable-mechanisms.png}
\caption{Performance of each mechanism (left) and building
consistency/durability guarantees (right) for 100K files creates from a single
client. Results are normalized to the runtime of writing events to the client's
in-memory journal.  \label{fig:composable-mechanisms}}
\end{figure}
